\documentclass[letterpaper,12pt]{article}

  %-----------------------------------------------------------
  \usepackage[empty]{fullpage}
  \usepackage{color}
  \usepackage[document]{ragged2e}
  \usepackage{textcomp}
  \definecolor{mygrey}{gray}{0.80}
  \raggedbottom
  \raggedright
  \setlength{\tabcolsep}{0in}
  
  % Adjust margins to 0.5in on all sides
  \addtolength{\oddsidemargin}{-0.5in}
  \addtolength{\evensidemargin}{-0.5in}
  \addtolength{\textwidth}{1.0in}
  \addtolength{\topmargin}{-0.5in}
  \addtolength{\textheight}{1.0in}
  
  %-----------------------------------------------------------
  %Custom commands
  \newcommand{\ts}{\textsuperscript}
  \def\CC{{C\nolinebreak[4]\hspace{-.05em}\raisebox{.4ex}{\tiny\bf ++ }}}
  \newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
  \newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
  \newcommand{\ressubheading}[4]{
    \begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-6pt}}
  \newcommand{\resprojectsubheading}[2]{
    \begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{#2} \\
    \end{tabular*}\vspace{-6pt}}
  %-----------------------------------------------------------
  
  %-----------------------------------------------------------
  %Variable declarations
  
  %Include High School Info
  \newif\ifhighschool
  %\highschooltrue
  
  %Include Not So Imp
  \newif\ifincludenotsoimp
  \includenotsoimptrue
  
  %Include Skills
  \newif\ifskills
  %\skillstrue
  \skillsfalse
  
  %Include Leadership Info
  \newif\ifprojects
  %\projectstrue
  \projectsfalse
  
  %Include Leadership Info
  \newif\ifleadership
  %\leadershiptrue
  \leadershipfalse
  
  %Include One Page
  \newif\ifonepage
  %\onepagetrue
  
  \ifonepage
  \objectivefalse
  \highschoolfalse
  \includenotsoimpfalse
  \skillsfalse
  \leadershipfalse    
  \fi
  %-----------------------------------------------------------
  
  \begin{document}
  
  \begin{center}
    \textbf{\Large Adnan Shaikh}
  \end{center}
  
  \begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
  
    C-1/904, Bramha Majestic & +91 9960 838 580 (mobile)\\
    NIBM Road, Kondhwa & adnan.shaikh1806@gmail.com \\
    Pune, MH, India & June 18, 1995\\
    411048 & www.adnanshaikh.com\\
  \end{tabular*}
  
  \vspace{0.1in}
  
  \resheading{Work Experience}
  \begin{itemize}
  \item
    \ressubheading{Persistent Systems}{Pune, India}{Software Engineer}{Jul. 2017 - Present}
    \begin{itemize}
      \resitem{Ported Sentient's agent-less client from Java to \CC to improve runtime performance and reduce its memory footprint.}
      \resitem{Solved major critical crashes and refactored major portions of the codebase to increase the reliability of the system.}
      \resitem{Converted the client from a console application to a Win32 service.}
      \resitem{Created Windows Installer (MSI) merge modules and installers using InstallShield along with build automation scripts.}
      \resitem{Modelled various sequence diagrams of the system to add to its documentation.}
      \resitem{Worked in an agile team using Scrum methodologies.}
    \end{itemize}
  \item
    \ressubheading{Persistent Systems}{Pune, India}{Academic Intern}{Aug. 2016 - Dec. 2016}
    \begin{itemize}
      \resitem{Designed and implemented an agent-less approach for an end point detection and response solution, in order to get the real time status of nearly 10,000 cross platform enterprise endpoints.}
      \resitem{Increased query throughput by nearly 3x by implementing a thread safe cache to reduce authentication requests.}
      \resitem{Wrote a Windows DLL in \CC to interface COM/DCOM functions over to Java using the Java Native Interface.}
      \resitem{Implemented various queries such as security, system alerts, hardware details, running processes, etc. as per the design specification.}
    \end{itemize}
  \item
    \ressubheading{Persistent Systems}{Pune, India}{Summer Intern}{Jun. 2015 - Aug. 2015}
    \begin{itemize}
      \resitem{Worked on reducing the lexical ambiguity and the global name space burden of Python 3.}
      \resitem{Extended Python 3 by providing support for Devanagari numbers and various Unicode math characters.}
      \resitem{The modified CPython source is capable of doing math in Devanagari numbers and supports math operators in Unicode like union, intersection, subset, etc.}
    \end{itemize}
  \end{itemize}
  
  \resheading{Education}
  \begin{itemize}
  \item
    \ressubheading{Vishwakarma Institute of Technology}{Pune, India}{Bachelor of Technology in Computer Engineering}{Jul. 2013 - May 2017}
    \begin{itemize}
      \resitem {Graduated 1\ts{st} Class with Distinction}
      \resitem {Major Project: Grammar correction using a Recurrent Neural Network}
      \resitem{Relevant Coursework: Design \& Analysis of Algorithms, Theory of Computation, Artificial Intelligence, Operating Systems, Distributed Computing, Business Intelligence}
    \end{itemize}
    \ifhighschool	
  \item
    \ressubheading{Delhi Public School}{Pune, India}{12th Grade CBSE}{May 2013}
    \begin{itemize}
      \resitem{Percentage: 76.4\%}
    \end{itemize}
  \item
    \ressubheading{Delhi Public School}{Pune, India}{10th Grade CBSE}{May 2011}
    \begin{itemize}
      \resitem{CGPA: 8.6}
    \end{itemize}
    \fi
  \end{itemize}
  
  \pagebreak
  
  \ifprojects
  \resheading{Projects}
  \begin{itemize}
  \item
    \resprojectsubheading{Source Code Project Visualizer}{Sep. 2017}
    \begin{itemize}
      \resitem{A source code browser written in Python 3 that displays the structure of a C++ code base and its include dependencies in an interactive visual graph displayed using Javascript.}
    \end{itemize}
  \item
    \resprojectsubheading{Text Amend}{May 2017}
    \begin{itemize}
      \resitem{An application that amends text using a recurrent neural network that can correct a subset of grammatical errors written in English. Written in Python using Google's TensorFlow library.}
    \end{itemize}
  \item
    \resprojectsubheading{adnanshaikh.com}{Dec. 2016}
    \begin{itemize}
      \resitem{Built my website using HTML5 and JavaScript to emulate a terminal interface. Built the accompanying blog with Ghost and Buster.}
    \end{itemize}
  \item
    \resprojectsubheading{Game Engine}{Jun. 2016 - Present}
    \begin{itemize}
      \resitem{Currently working on a game engine written in C++ using the OpenGL API. Supports the following features: free-roaming FPS camera, .obj object file loading, texture loading and phong lighting.}
    \end{itemize}
  \item
    \resprojectsubheading{Genetic Image Re-creator}{May 2016}
    \begin{itemize}
      \resitem{The application recreates an image by generating a random population of images, each consisting of randomly transformed and colored triangles. Breeds the top 2 images closest to the source image to form a new population of images with random mutations following the process of genetic evolution. Implemented using the GTK+ toolkit and C.}
    \end{itemize}
  \item
    \resprojectsubheading{Travelling Salesman Problem Solver Simulator}{Dec. 2015}
    \begin{itemize}
      \resitem{Written in Python 3, implemented various solutions: Dynamic Programming, nearest neighbor, heuristic algorithms namely 2-opt and 3-opt and interfaced them with the Tkinter GUI kit.}
    \end{itemize}
  \end{itemize}
  \fi
  
  \ifskills
  \resheading{Skills}
  \begin{description}
  \item[Languages:]
    C/C{}\verb!++!, Java, Python, Bourne Shell
  \item[Tools:]
    MS Visual Studio, SVN, Git, Emacs, Make, Maven
  \item[Miscellaneous:]
    Great troubleshooting and debugging skills
  \end{description}
  \fi
  
  \ifleadership
  \resheading{Organizations}
  \begin{itemize}
  \item
    \ressubheading{Geekfest Pune}{Pune, India}{Co-founder}{Sep. 2014 - Present}
    \begin{itemize}
      \resitem{Co-founded an annual not-for-profit event to bring together creative people who share a passion for art, design, technology, literature, etc. to share well-formed ideas, interact and connect with each other.}
      \resitem{More than 60 attendees in the first edition, followed by 110 attendees in its second year.}
    \end{itemize}
  \item
    \ressubheading{AIESEC in Pune}{Pune, India}{Team Leader of Business Development}{Aug. 2014 - Jul. 2015}
    \begin{itemize}
      \resitem{Worked on gathering sponsorships for organizing an annual stakeholders\textquotesingle \ summit dubbed NEXUS’.}
      \resitem{The event aimed towards bringing the clients and stakeholders of AIESEC in Pune to gather around to discourse the theme of the evening and network with each other.}
      \resitem{Dealt with HR heads to help their organization hire globally competent \& requirement specific employees.}
    \end{itemize}
  \end{itemize}
  \fi
  
  \end{document}